%Stuck-at-patterns V.S. Cell-Aware Top 

%non functional requirements are those that can be used to judge the operation of a system 

%One of the first things that the graph above illustrates is that the number of non-functional test patterns decreases with as the 
%number of repetetive detects. This means that although n-detect might be helpful in order to determine the number of functional faults
%that the number of non-functional faults cannot be detected as easily by increasing the numbe of redundant fault checks. Thus, it becomes 
%aparant that the lower the number of redundant checks in the n-detect pattern set this higher the number of patterns that test the non-functional
%faults. So in order to test for non-functional faults the pattern set size, along with the test time, can be decreased by using no redundant detection.
%In other words using n0 can increase the non-functional coverage while also cutting the costs of using more redundancy with a higher n-detect pattern set. 

%%%%% All Cell-aware faults here we mentioned are not detected by stuck-at ATPG
% Page 1:
%  (1) two fault set and two differnet 10k Good-state patterns got similar results:
%  (2) # of  Non-functional patterns are more than # of functional patterns obviously, even compare with # of stuck at ATPG, it also need to add more patterns obviously, 
%  (3) but # of functional patterns V.S. # of stuck at ATPG are not very siginificantly
%  (4) Hence, we drop Non-functional patterns only add Functional patterns, we can save siginificantly costs ( time and money)
%  (5) With Multi-N-detecton functon increase,  # of  Non-functional patterns is decreasing, but not siginificantly, so,  Multi-N-detecton is helpful for saving Cell-aware fault patterns, but not too much


% Page 2:
%  (1) Equation %= # of non_functional Cell_Aware faults patterns/(stuck_at ATPG + # of funtional Cell_aware patterns)
%  (2) two fault set and two differnet 10k Good-state patterns got similar results:
% (3) With Multi-N-detecton functon increase,  % of  Non-functional cell-aware test patterns is decreasing, but when n = 3, it still remains 3%~4%, and also this decreasing is coming from the number of stuck-at ATPG increas, its real number of patterns are not dereased siginificantly (we can see in Page1)

% Page 3:
%  (1) Equation
%       (a)non_functional = # of non_functional Cell_Aware faults /(# of non_functional Cell_Aware faults+ # of functional Cell_Aware faults)
%        (b)functional = # of functional Cell_Aware faults /(# of non_functional Cell_Aware faults+ # of functional Cell_Aware faults)
%  (2) two fault set and two differnet 10k Good-state patterns got similar results:
%  (3) the non-functional Cell-Aware faults accounted for a large proportion of total of  Cell-aware faults which not detected by stuck-at ATPG
%  (4) The worst case on s12307, it accounts 100%~97%
%  (5) The best case on s38584, it still accounts 50%~55%

% From those figures(Page1~Page3), drop non-fuctional Cell-Aware faults can siginificantly enhance faults testing efficiency

%Page4, the table1
% (1) This table shows # of the funtional faults in each cicuit
% (2) The bigger circuit, the more functional faults

% Other figures in page4 and page 5
% (1) those figures are shown the number of detections for each fault mentioned in Table1
% (2) The X axis represents the each functional fault  (The order is AND=>NAND=>NOR=>OR, the input pins 2=>3=>4)
% (3) some faults are detected very lowest(1~2 times), some are largest (8000 times), those larger number of detected faults are most important for testing
% (4) Multi- N- dectection funciton cannot detected many functional faults even n increase, some of those faults are most important for testing





%%%%%%%%%%%%%%%%%%%%%%PAGE 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\begin{document}

In the above figures we can see that two different generations of 10\,000 good-states used on two different permutations of a UDFM(User Defined Fault Model) yielded similar results. Another observation is that in each of the four cases there are more patterns that test for non-functional defects than those that tests for functional defects that are generated by cell aware ATPG, even in comparison with the large number of patterns generated by stuck-at ATPG, the number of non-functional patterns is significant. The number of functional test patterns is negligible compared to the large amount of patterns generated by the stuck-at ATPG. Because adding all of the non-functional tests to the test set adds significant costs, these figures suggest that using n-detect with a higher degree of n can decrease the number of non-functional tests which will decrease the added costs associated with testing all of the non-functional defects. 

These graphs represent the total percentage of patterns that test for non-functional defaults generated by cell aware ATPG out of all of the total patterns for each of the five circuits that were tested. Here again we see that two different sets of 10\,000 good-states, as well as two different UDFM's achieved similar results. As the n-detect redundancy increases we see a sharp decrease in the percentage of patterns that check for non-functional defects. Although even when we use n3 there remains 3~4\% of patterns testing non-functional defects this is still a dramatic decrease from the normal percentage which is around 17~18\% of all test patterns. This percentage decrease is not due to a decrease in the actual number of non-functional test patterns(as seen in figure 1), but an overall increase in the number of stuck-at ATPG patterns generated in response to the desired functional test redundancy of the n-detect pattern generation. 

The above figures show the distribution of percentages of functional, and non-functional test patterns generated over all the patterns not generated by stuck-at ATPG. Once again the results were similar for all of the tested patterns and UDFMs. We can see that the non-functional test patterns that were generated accounted for a large percentage of the total patterns that were generated by cell aware ATPG. In s13207 the non-functional test patterns accounted for 97-100\% of all the cell aware generated patterns, whereas in s38584 non-functional test patterns only accounted for 50-54\% of the total cell aware generated patterns. 

This table shows the number of functional faults in each circuit, because faults are inserted in each of the gates we can see that the larger the circuit, the more faults are inserted.

Here are charts for each of the five circuits that were tested. They show the number of functional faults that were detected based on the UDFM used and the iteration of the test. The bars above each of the n-detect numbers represent the faults detected in each set of gates: AND, NAND, NOR, and OR respectively, with 2,3, and 4 input pins each. We noticed that some faults were detected only 2 or 3 times, whereas others were detected as many as 8\,000 times. The faults that were detected many times are likely the most crucial faults. N-detect does not detect many important functional faults, even as n increases. This suggests that increasing the redundancy of the test set with n-detect is ineffective for examining these crucial functional faults.  

\end{document}



















